---
title: "How to mange CWB weather data"
author: "YiChun Sung"
date: "2017年4月25日"
output: 
  html_document:
    toc: true
    toc_float: true
---
### Packages

R is the famous statistics language ,so you can use your favorite package which you can chosoe by yourself. Because of diversity of packages, many data scienists usually create their style packages. 

通常使用R 語言時，各資料分析者都會使用自己順手的套件協助處理當前的工作，因此套件多樣化也是R語言的特長。
各資料分析者或資料科學家也常將自己處理的工作流程製作成好用的套件提供其他使用者使用，達到教學相長的目的。
```{r eval=FALSE}
# Library Packages
library(magrittr)
library(httr)
library(rvest)
library(stringr)
library(reshape2)
library(knitr)

```


```{r echo = FALSE}
# 將資料夾裡所有的.csv檔案讀取進來
fileList <- list.files(path = "C://testDOC/", pattern="*.csv")
for (i in 1:length(fileList)){
  assign(fileList[i], 
         read.csv(paste("C://testDOC/", fileList[i], sep=''))
  )}

```

### Reading .csv

此外，R語言的優點在於能夠處理相當多種不同的資料格式，從.txt檔、.csv檔、.xlsx檔、.json檔甚至可以處理.shp或是圖片檔等等。

而這裡我從外部將氣象局各測站的基本資料讀取進來，氣象局各測站資料也是利用爬蟲程式抓取的。

```{r stationList}

stationList <- read.csv("data/new_Station_List.csv")

inputStationName <- c("Beiliao") # "Location" # station

```


### input Date 

In this part, we need a time sequence. After we bulid a time sequence, we can get CWB data in the time which we choosed.
as.Date is a good function that can let us bulid a time sequence.

在這一部分，我們需要生產一個時間序列，根據排序，我的程式會一個一個抓取該日期的資料下來。
as.Date函數 可以在兩個你自由選擇的時間區間內生產一個時間序列。
```{r lengthDate}

fromdate <- as.Date("2017-01-06") # "2017-01-06" # timerange1
todate <- as.Date("2017-01-06") # "2017-01-06"  # timerange2
date <- seq.Date(fromdate, todate, "day")
lengthDate <- as.numeric(length(date))
lengthDatep <- as.numeric(lengthDate+1)
  
```

### url

According CWB website, we know the data from CWB is dispaly in one page for single day.
Then, we bulid a data frame to mange our url for each day. 
接著，我們生產一個data.frame去裝每一個日期所對應的url。

```{r subdataframe}
url_1 <- "http://e-service.cwb.gov.tw/HistoryDataQuery/DayDataController.do?command=viewMain&station="
url_2 <- "&stname=%25E7%25AB%25B9%25E6%259D%25B1&datepicker="
url_1_1 <- paste(url_1, stationList$id, sep = "")
url_all <- paste(url_1_1, url_2, sep = "")
stationListnew <- cbind(stationList, url_all)
  
substation <- data.frame(subset(stationListnew, stationListnew$engName == inputStationName))
subdataframe <-data.frame(date=date, urldate = paste(substation$url_all, date ,sep=""))

```


### Xpath data

找到每一個欄位的xpath。

```{r xpathSelect_result}
inputxpathName <- c("press") # "ex: press" # iterm
  
  # Rain
xpathrain <- "//table[@id='MyTable']/tbody/tr/td[11]" # Xpath for rain data
  
  # Hum
xpathHum <- "//table[@id='MyTable']/tbody/tr/td[6]" # Xpath for RH data
  
  # Tem
xpathTtem <- "//table[@id='MyTable']/tbody/tr/td[4]" # Xpath for Temperature data
  
  # Press
xpathPres <- "//table[@id='MyTable']/tbody/tr/td[2]" # Xpath for StnPres data
  
XpathName <- c("Rain", "Hum", "Tem", "Press")
  
xpathurl <- c(xpathrain, xpathHum, xpathTtem, xpathPres)
  
xpathList <- data.frame(XpathName, xpathurl)
  
xpathselect_dataframe <- subset(xpathList, xpathList$XpathName == inputxpathName)
  
xpathSelect_result <- as.vector(xpathselect_dataframe$xpathurl)
xpathList

```

### Get the data!

```{r eval=FALSE}
hr24 <- data.frame(Hour=1:24) # set one day time
  
  for (i in 1:lengthDate){
    urlhtml <- as.vector(subdataframe$urldate[i])# as.vector(date_dataFrame$urldate[1])
    # doc <- read_html(urls)
    datadoc <-read_html(urlhtml)# read_html(as.vector(date_dataFrame$urldate[1]))
    data <- datadoc %>%
      html_nodes(., xpath = xpathSelect_result)%>%
      html_text
    data_renew <- str_trim(sub("<U+00A0>",replacement ="",data)) # Delete something we don't need
    hr24 <-cbind(hr24, data_renew)
    
  }
  names(hr24)[2:lengthDatep] <- as.vector(as.factor(date))
  hr24_all <- melt(hr24, id=c("Hour") ) # Let them for one column
  names(hr24_all) <- c("hour", "date", "data")
  POStime <- as.POSIXct(paste(hr24_all$date, hr24_all$hour, sep = " "), "%Y-%m-%d %H", tz="GMT")
  resultTable <- data.frame(time=POStime, data= hr24_all$data)
  names(resultTable)[2] <-c(iterm)
  

```

### Buliding a function

finally, we can bulid a function that we can use this function to quickly mange CWB data.
In the future, we won't need to tyoe a lot of codes and easy to bulid data frame.

```{r, message=FALSE, warning=FALSE}


getDataformCWB <- function(station, timerange1, timerange2, iterm){
  # Library packages
  library(magrittr)
  library(httr)
  library(rvest)
  library(stringr)
  library(reshape2)
  library(knitr)
  # ---------- input Targat Station ---------- #
  # Load Station List
  
  stationList <- read.csv("data/new_Station_List.csv")
  
  inputStationName <- c(station) # "Location"
  
  
  # ---------- input Date ---------- #
  fromdate <- as.Date(timerange1) # "2017-01-06"
  todate <- as.Date(timerange2) # "2017-01-06"
  date <- seq.Date(fromdate, todate, "day")
  lengthDate <- as.numeric(length(date))
  lengthDatep <- as.numeric(lengthDate+1)
  
  
  # ---------- URL ---------- #
  url_1 <- "http://e-service.cwb.gov.tw/HistoryDataQuery/DayDataController.do?command=viewMain&station="
  url_2 <- "&stname=%25E7%25AB%25B9%25E6%259D%25B1&datepicker="
  url_1_1 <- paste(url_1, stationList$id, sep = "")
  url_all <- paste(url_1_1, url_2, sep = "")
  
  stationListnew <- cbind(stationList, url_all)
  
  substation <- data.frame(subset(stationListnew, stationListnew$engName == inputStationName))
  subdataframe <-data.frame(date=date, urldate = paste(substation$url_all, date ,sep=""))

  # ---------- Xpath ---------- #
  inputxpathName <- c(iterm) # "ex: press"
  # Rain
  xpathrain <- "//table[@id='MyTable']/tbody/tr/td[11]" # Xpath for rain data
  # Hum
  xpathHum <- "//table[@id='MyTable']/tbody/tr/td[6]" # Xpath for RH data
  # Tem
  xpathTtem <- "//table[@id='MyTable']/tbody/tr/td[4]" # Xpath for Temperature data
  # Press
  xpathPres <- "//table[@id='MyTable']/tbody/tr/td[2]" # Xpath for StnPres data
  
  XpathName <- c("Rain", "Hum", "Tem", "Press")
  
  xpathurl <- c(xpathrain, xpathHum, xpathTtem, xpathPres)
  
  xpathList <- data.frame(XpathName, xpathurl)
  
  xpathselect_dataframe <- subset(xpathList, xpathList$XpathName == inputxpathName)
  xpathSelect_result <- as.vector(xpathselect_dataframe$xpathurl)
  
  #-----
  
  hr24 <- data.frame(Hour=1:24) # set one day time
  
  for (i in 1:lengthDate){
    urlhtml <- as.vector(subdataframe$urldate[i])# as.vector(date_dataFrame$urldate[1])
    # doc <- read_html(urls)
    datadoc <-read_html(urlhtml)# read_html(as.vector(date_dataFrame$urldate[1]))
    data <- datadoc %>%
      html_nodes(., xpath = xpathSelect_result)%>%
      html_text
    data_renew <- str_trim(sub("<U+00A0>",replacement ="",data)) # Delete something we don't need
    hr24 <-cbind(hr24, data_renew)
    
  }
  names(hr24)[2:lengthDatep] <- as.vector(as.factor(date))
  hr24_all <- melt(hr24, id=c("Hour") ) # Let them for one column
  names(hr24_all) <- c("hour", "date", "data")
  POStime <- as.POSIXct(paste(hr24_all$date, hr24_all$hour, sep = " "), "%Y-%m-%d %H", tz="GMT")
  resultTable <- data.frame(time=POStime, data= hr24_all$data)
  names(resultTable)[2] <-c(iterm)
  return(resultTable)
}

Zhudong_Press <- getDataformCWB("Zhudong", "2016-03-14", "2016-03-19", "Press")
library(knitr)
kable(Zhudong_Press[1:20, ], caption = "Zhudong Press data")
#Zhudong_Press
```
